Dusty galaxies and the degeneracy between their dust distributions and the attenuation formula

### 2015-04-28 response.txt

We clarify our discussion of the uniform screen model in the
Introduction. k(lambda) is an empirical equation; predictions of
attenuation values from k(lambda) do assume a dust distribution.

* First paragraph of Sect. 2.2.3. The K98 IR estimator actually assumes
that the galaxy is totally buried into dust. Therefore, combining the UV
with the TIR directly can be a dangerous game (though quite common in
the literature). As UV is detected, galaxies are not that strongly
attenuated so the assumption does not hold and the dust heating sources
are not the same anymore, which in turn should change the calibration
coefficient. Also, the listed assumptions are not enough in my opinion.
Even if the SFR is constant over 10^8 years, the Halpha and UV+IR SFR
would not be the same, because of contamination by stars older than 100
Myr in the UV but not in Halpha. As possible biases in the derivation of
the SFR would have a direct impact on the results, I suggest that they
are fully taken into account and properly discussed in the paper. In any
case, beyond that, assuming in effect that SFR(Halpha)=SFR(UV+TIR) is a
very strong assumption. If there is a tiny wiggle of the SFR in the last
few Myr, that is sufficient to throw the different SFR completely off
from one another. As said just above, the results of this paper are
sensitive to such effects. I think it is therefore especially important
that the impact of such variations is discussed in more detail than in a
lone paragraph in Section 4.

We agree that determinations of star formation rates are fraught with
uncertainty. Attenuation does not have to decrease with increasing UV
emission: galaxies may have one set of star forming regions which are
totally buried and another set which are totally exposed.  Many papers
discuss in much detail the assumptions made by those who convert
luminosity to star formation rate.  K98 and the review article by Madau
& Dickinson, which we cite in section 4, mention many of these same
issues.

An extended discussion on our part can be arbitrarily complex---for
example, some in the stellar community might argue that we don't know
even the evolution of the ionizing luminosity of a simple stellar
population (Sana et al. 2012); some in the extragalactic community might
argue that we're extrapolating a total infrared luminosity from two or
three flux densities.  Our assumptions are strong but we do acknowledge
them.  In our view these important details have deserved their own
papers.

@@

* "The arrangement of dust is often described, oddly, as its geometry".
I am not sure what is particularly odd in that. But more precisely, what
is described is the relative arrangement of dust relative to stars as
this is one of the major parameters that govern the actual impact of
dust on the emerging radiation.

We removed this statement.

* "If we want to learn about galaxies, morphology should be a
wavelength-independent word". Should it? I do not see why. The
differences in morphologies in different bands are extremely informative
on the physics of galaxies.

We say that morphology should be a wavelength-independent word.  We do
not say that morphology itself is independent of wavelength.  In our
view the community reserves the word morphology for "what we see at
visible wavelengths."

@@

* "An attenuation formula is denoted k(lambda) or k'(lambda)." I do not
think this statement is useful here. First the term "attenuation
formula" is extremely vague. Then, unless I am mistaken, k is not used
in any meaningful way elsewhere in the paper anyway.

We expanded our discussion of k'(lambda).

* "A low-redshift galaxy [...] underestimates the measured Halpha
attenuation." Please back this with a reference.

The relevant citations come at the end of the next sentence: Calzetti et
al. 94 and 97b.

@@

* "If we choose to think of dust distributions as clumpy [...] 60% of
the number of clumps surrounding ionizing stars (Calzetti+97a)". Once
again, I do not see where the mentioned paper cites that number. If it
is indeed that paper: http://de.arxiv.org/abs/astro-ph/9706121 then the
word clump is not even mentioned even once in the paper. Please clarify
this part.

The referee has an incorrect link.  The paper we cite is: Calzetti, D.
1997, AJ, 113, 162.

* "if we consider that galaxies have centers and outskirts." That
statement is odd. Any spatially bounded object has outskirts.

Any spatially bound object has outskirts but they are not always
considered. We added a sentence.

@@

* Price+13 should be Price+14.

Corrected.

* About the correction for the NII contamination, which should be
metallicity dependent, what about using a mass-metallicity relation for
instance? That would be far from perfect but certainly better than
assuming a constant [NII]/Halpha.

Weiner et al. 2007 have a sample of galaxies with -23 < M_H < -21 for
which the average correction is roughly constant.  This is the basis for
our correction.

@@

* Editorial question, it looks odd that the second author of the paper
is cited for data provided as "private communication".

We don't know how else to cite the data.

* Sect. 2.2.1, second paragraph. Maybe I am misunderstanding what is
written, but it appears to say that fitting the CE01 templates on the 24
micron band only will overestimate the 70 and 100 micron fluxes (and
therefore most likely it will also overestimate the TIR), and that the
TIR found in the paper is even higher. If it is the case, I find that
very worrisome. If it is not the case, please clarify this paragraph to
remove ambiguities.

We use the CE01 templates for all samples in the paper to be consistent.
We have presented results based on both our luminosities and the
luminosities from Overzier et al. 2011.

@@

* The TIR luminosities of the so-called dust-poor and dusty galaxies are
not that different. This suggests some possible selection effects. This
aspect should be discussed in detail in the paper.

The UV luminosities are different.  We have discussed the origins of the
low-redshift samples.

@@

* The title of Sect. 3.1 is unclear. One would wonder what "relation" is
considered here.

Clarified.

* Sect. 3.1, it would be useful to specify what exactly is the "low
redshift IRX-beta relation".

We are unsure what the referee means by "exactly."  Our subsequent
sentences explain the IRX-beta relation.

@@

* Last paragraph of Sect. 4. This assumes that the stars and the gas
follow the same attenuation law. This may or may not be the case.
Calzetti considers that this is not the case. Also later in that
paragraph, I may be missing something, but I do not understand why this
would prove that SFH are correct. Just after the authors rightly mention
that f(Halpha)/f(Hbeta) is SFH-independent. So this test just does not
tell us much of anything regarding the SFH I think. Please clarify.

We have mentioned and clarified these assumptions in the text.

* As a final note, here is the assessment by a statistical expert on the
fitting done in the paper: The choice of regression methodology in Fig 4
is unclear to me. Why do the orange lines seem constrained to pass
through the origin? The resulting fit for the top right diagram, for
example, is clearly poor. Statisticians would recommend that, when
heuristic (e.g. linear) parametric models fit poorly, that nonparametric
local regression methods be used to show the true behavior of the
bivariate relationship. There are various methods -- splines, LOESS,
kriging (= Gaussian process regression) -- some of which give local
confidence bands. Several recent texts are available; e.g. K.Takezawa
`Introduction to Nonparametric Regression'. For implementation in the
public R statistical software environment, see a tutorial on density
estimation at http://www2.astro.psu.edu/users/edf/Caltech_2014.

The problem with nonparametric regression methods lies in the
interpretation. We choose to fit through the origin because we want our
model to lack dust around Ha emitting regions when there is no dust
around UV emitting regions. A very basic prediction of the attenuation
formula is that if the escape fraction is 1 at any wavelength it is 1 at
all wavelengths.  Another basic prediction is that if the escape
fraction is less than 1 at any wavelength it is less than 1 at all
wavelengths.

We mention a reason for the poor fit to the low-redshift dusty galaxies
in section 3.4.  This section existed previously; we divided section 3.3
into two sections for clarity.

### 2015-04-28 paper.tex
Final edits?

%\newcommand{\alephuv}{\textphnc{\ARaleph}$_{\mathrm{UV}}$}
%\newcommand{\alephha}{\textphnc{\ARaleph}$_{\mathrm{H}\alpha}$}
%\newcommand{\alephuvha}{\textphnc{\ARaleph}$_{0.66}$}
%\newcommand{\alephhb}{\textphnc{\ARaleph}$_{\mathrm{H}\beta}$}
\usepackage{lscape}
\newcommand{\alephuv}{f$_{\mathrm{esc}}$(0.16$\,\micron$)}
\newcommand{\alephha}{f$_{\mathrm{esc}}$(H$\alpha$)}
\newcommand{\alephuvha}{f$_{\mathrm{esc}}$(0.66$\,\micron$)}
\newcommand{\alephhb}{f$_{\mathrm{esc}}$(H$\beta$)}

@@

\altaffiltext{1}{Laboratoire AIM, DSM/Irfu/SAp, CEA-Saclay,
91191 Gif-sur-Yvette, France}
\altaffiltext{2}{National Optical Astronomy Observatory,
Tucson, AZ 85719, USA}
\altaffiltext{3}{Department of Astronomy, University of Arizona,
Tucson, AZ 85721, USA}
\altaffiltext{4}{Laboratoire d'Astrophysique de Marseille, Aix
Marseille Universit\'e, 13388 Marseille cedex 13, France}
\altaffiltext{5}{Department of Astronomy, University of California Riverside,
Riverside, CA 92521, USA}
\altaffiltext{6}{Space Telescope Science Institute, Baltimore, MD 21218, USA}
\altaffiltext{7}{Department of Physics \& Astronomy, Texas A\&M University,
College Station, TX 77843, USA}
\altaffiltext{8}{Department of Astronomy, University of Massachusetts Amherst,
Amherst, MA 01003, USA}

@@

A galaxy's morphology is often defined as its spatial distribution of stars.
Rest-frame optical images of galaxies show diverse arrangements of
their stellar components: smooth ellipticals, tightly-wound spirals, clumpy
disks, barred disks, train-wrecks, fuzzballs, and whatever Willman 1 is.
Little more than spatial extent is known about distributions of dust in dusty
galaxies
\citep{younger10,diaz10,simpson15}.  (The arrangement of
dust is often described, oddly, as its geometry.)  Yet spatial distributions of
all galactic components have intrinsic value.  If we want to learn about
galaxies, morphology should be a wavelength-independent word.  Surprises
surely abound: for example, galaxies at $z \sim 0.3$ have dust out to several
Mpc.  Their average dust mass profile is a constant fraction of their average
halo mass profile \citep[][see also \citealt{zaritsky94}]{menard10}.

@@

If we write an equation like this:

\begin{math}
L_{\mathrm{emergent}}/L_{\mathrm{intrinsic}} = 10^{-\mathrm{A}/2.5} = 10^{-\mathrm{E(B-V)} k(\lambda)/2.5}
\end{math}

we assume a uniform screen not because $k(\lambda)$ is solely dependent on
wavelength, but because $L_{\mathrm{emergent}}/L_{\mathrm{intrinsic}}$ is solely
dependent on
wavelength.  In an illustrative sense
$L_{\mathrm{emergent}}/L_{\mathrm{intrinsic}}$
is an attenuation formula convolved with a spatial distribution of dust.

@@

The discrepancy between the uniform assumption and real dust
distributions in low-redshift dust-poor galaxies grows even larger if we
consider that galaxies have centers and outskirts.  A number of studies find
that H$\alpha$ and UV attenuation decrease with increasing radius
\citep{boissier04,prescott07,munoz09}.  Ionizing stars are surrounded by more
dust than nonionizing UV-emitting stars; ionizing stars
at large radii have less dust than ionizing stars at small radii, and similarly
for nonionizing UV-emitting stars.

@@

Our study uses observations of the GOODS-S, COSMOS, and UDS regions.  A
catalog of \emph{Herschel}/PACS 100$\,\micron$ sources for GOODS-S comes from
\citet{magnelli13}; for COSMOS and UDS, we use catalogs produced for the
\emph{Herschel} survey of CANDELS regions (Inami et al., in prep).  A
100$\,\micron$ source is defined as a $\ge 3\sigma$ flux density measurement
from PSF fitting to a \emph{Spitzer}/MIPS 24$\,\micron$ source, which is based
on an IRAC 3.6$\,\micron$ source prior.  In GOODS-S, the catalog has
flux densities at 24, 70, 100, and 160$\,\micron$; in COSMOS and
UDS, the catalogs have flux densities at 24, 100, 160, 250, 350,
and 500$\,\micron$.  All flux densities are $\ge 3\sigma$.  We do not use the
250, 350, and 500$\,\micron$ flux
densities in the COSMOS and UDS catalogs, to avoid the effects of source
confusion on PSF fitting.  (Including them changes our results negligibly.)

@@

Some sources will be at $0.7 < z < 1.5$ but will not have visible H$\alpha$
line flux.  To determine line flux upper limits for these sources, we match each
100$\,\micron$ source to a source with a spectroscopic redshift in
the catalogs of: \citet{lefevre04,szokoly04,mignoli05,yamada05,ravikumar07,
vanzella08,lilly09,balestra10,fadda10,simpson12,kurk13,santini14}; Simpson et
al. (in prep.); Almaini et al. (in prep.); and
M. Dickinson (private communication).  (Operationally both the
100$\,\micron$ and spectroscopic catalogs are matched to the CANDELS catalogs.)
If the 100$\,\micron$ source has a spectroscopic redshift that is unconfirmed
by an uncontaminated grism spectrum, we estimate the widths of the invisible
Gaussian line profiles from the ratio of integrated flux density to peak
surface brightness for the region of the direct image surrounding the galaxy.
(The direct
image is the image taken as part of the grism observations.)  We then fit
the same model as above to the 1D spectrum and extract the H$\alpha$ line flux
uncertainty.  We use $5\sigma$ limits.  We are unable to determine limits for
galaxies observed by the grism that are undetected in the direct image.  Most
limits are in GOODS-S because the spectroscopic completeness is higher there
than it is in COSMOS or UDS.

@@

We use 24$\,\micron$ flux densities in the \emph{Spitzer} Heritage Archive.  Of
the 26 sources in \citet{overzier11}, 3 have unreliable 24$\,\micron$ flux
densities (per the recommendations in the enhanced imaging products quick start
guide); these sources are excluded.  The remaining 23 galaxies have flux
densities at
0.15 and 0.23$\,\micron$ (NUV and FUV bands), from \emph{GALEX} observations.
H$\alpha$ line
fluxes, from SDSS observations, are from Overzier (private communication).  We
multiply the line fluxes by 1.67 as a fiber-aperture correction
\citep{overzier09}.

@@

We must exclude galaxies with active nuclei because fractions of their IR,
emergent UV, and emergent H$\alpha$ luminosities will be unrelated to newly
formed massive stars.  We identify 5 AGN hosts among the high-redshift dusty
galaxies; we use the \citet{donley12} criteria, which are based on mid-IR flux
densities (which all 3 CANDELS catalogs have).  These criteria will miss some
AGN hosts \citep{juneau13}.  We accept the contaminants because in some fields
we lack data---for example, X-ray data---that we could use to identify the
missed AGN hosts.

@@

Three star formation rates allow us to compare two attenuation values.
We eschew magnitude attenuation in favor of the escape fraction, which
is the ratio of emergent to intrinsic luminosity.  We define the following
quantities.
\begin{itemize}
\item \alephuv~is the escape fraction at rest-frame 0.16$\,\micron$.  (In
relation to A$_{\mathrm{UV}}$,
f$_{\mathrm{esc}}$(0.16$\,\micron$) = 10$^{-\mathrm{A}_{\mathrm{UV}}/2.5}$.)
\item \alephha~is the escape fraction of the H$\alpha$ line luminosity.
\item \alephuvha~is the escape fraction extrapolated from \alephuv~to the
wavelength of H$\alpha$---the attenuation formula prediction.  For the
attenuation formula in \citet{calzetti00}, \alephuvha~= \alephuv$^{0.33}$.
\end{itemize}

@@

\subsection{Reproducing the relation for dust-poor galaxies}

The sample, from \citet{overzier11}, contains galaxies that lie roughly on
the low-redshift IRX-$\beta$ relation.  This relation is a blunt instrument we
use to determine whether or not galaxies obey an attenuation formula at UV
wavelengths; \alephuv~is a function of IRX and an attenuation formula relates
\alephuv~to $\beta$.  Since these galaxies lie on the relation, we
expect them to have dust properties that conform with the properties of
the galaxies in the \citet{calzetti00} sample.  We calculate \alephha~and
\alephuv~for each galaxy in the following way.
\begin{itemize}
\item \alephuv~from IRX: \alephuv~= ($L_{\mathrm{IR}}$/($1.68\times0.16\times
L_{\mathrm{0.16}}$)+1)$^{-1}$.  (Equivalent to \alephuv~= [emergent UV
SFR]/[IR SFR + emergent UV SFR].)
%\item \alephuvha~= \alephuv$^{0.33}$.
\item Following the assumptions in \ref{sfrs}: \alephha~=
(emergent H$\alpha$ SFR)/(IR SFR + emergent UV SFR).
\end{itemize}
We use these quantities to find, for the sample, a best-fit power-law index $q$
for the form \alephha~= \alephuv$^{q}$.

The top left panel of Fig. \ref{fha_fuv} shows that \alephha~= \alephuv$^{0.80}$
for the low-redshift
dust-poor galaxies.  (If we use the IR and UV luminosities from
\citealt{overzier11}, \alephha~= \alephuv$^{0.84}$.)  We lack
uncertainties on any SFRs so we also perform a robust linear regression
(which requires a fit to the form $\log\,$\alephha~= $q\,\log\,$\alephuv).  It
returns a similar result, as does a bootstrap resampling.  We recover a relation
close to the
\citet{calzetti97b} relation for similar galaxies, so we have some confidence
that our procedure is grossly correct.  We stress, again, that there are
no evolutionary connections between the low- and high-redshift galaxy samples;
we aim only to reproduce the \citet{calzetti97b} result with our nonstandard
method of determining \alephha.

@@

The top right panel of Fig. \ref{fha_fuv} shows that \alephha~=
\alephuv$^{0.55}$ for the low-redshift
dusty galaxies.  We use uncertainties only on the emergent H$\alpha$-derived
SFR (we treat it as the dependent variable) in the weighted fit.  The relation
for dust-poor galaxies is seemingly inapplicable to dusty galaxies at
low redshift.  In \S\ref{subsec:highz} and \ref{sec:discuss} we explain why we
preface `inapplicable' with `seemingly.'

@@

The bottom left panel of Fig. \ref{fha_fuv} shows that \alephha~=
\alephuv$^{0.55}$ for high-redshift
dusty galaxies.  We leave limits out of this fit.  The uncertainty in
the index is very small; this is not surprising given the number of galaxies.
The dispersion about the best-fit relation is large; the central 50\% of
galaxies with H$\alpha$-detected SFRs lies between \alephha~= \alephuv$^{0.45}$
and \alephha~= \alephuv$^{0.66}$.  A survival regression, which incorporates
H$\alpha$ SFR limits in a fit to the form $\log\,$\alephha~=
$q\,\log\,$\alephuv, finds $q = 0.47$, as does a simple linear regression using
only the H$\alpha$-detected SFRs.  (None of the galaxies have limits for both
the UV and H$\alpha$ SFRs.)  The main effect of including limits in the
regression is to increase the standard error of the sample's best-fit index; a
marginally different index is a secondary effect.  Table \ref{regress}
summarizes the relevant quantities for the main fit to each sample of galaxies.

@@

@@

If we assume that dusty galaxies obey the \citet{calzetti00} attenuation
formula, our results indicate that their H$\alpha$ and 0.66$\,\micron$ escape
fractions disagree.  Unlike low-redshift dust-poor galaxies, dusty galaxies
have \alephha~= \alephuvha$^{1.6}$; like low-redshift dust-poor galaxies,
dusty galaxies have nonuniform dust distributions.  The relations between
\alephha~and \alephuvha~are similar to those found by \citet{onodera10},
\citet{kashino13}, and \citet{price13} and conflict with those of
\citet{erb06}.  These studies assume the applicability of the \citet{calzetti00}
attenuation
formula, and use samples of high-redshift galaxies that are not necessarily
dusty.  Their UV escape fractions come from stellar population modeling, while
ours come from IRX; their H$\alpha$ escape fractions come from ratios of
averaged H$\alpha$ to averaged H$\beta$ luminosities, or ratios of H$\alpha$ to
UV luminosities, while ours come from assumptions about SFRs.

@@

The dispersion about the best-fit relation for high-redshift dusty galaxies
is large, yet it is susceptible
to our possibly invalid assumption that a galaxy's instantaneous SFR has,
for at least $10^{8}$ yr, equaled its prolonged SFR.  For example, if most
massive stars formed over 15 Myr instead of 300 Myr, we should multiply
$L_{0.16}$ and $L_{\mathrm{IR}}$ by larger numbers than we do here to derive the
UV and IR SFRs.  The true UV SFR is 57\% higher and the true IR SFR is 63\%
higher \citep{madau14}.  The true UV escape fraction is little different;
because the true total SFR is higher, the true H$\alpha$ escape fraction is
lower.  (Another scenario is that massive stars stopped forming within the last
15 Myr.)  Perhaps some of the high-redshift dusty galaxies have
complicated star formation histories; the combined effect of deriving correct
SFRs might lead to lower dispersion.

>>>>

%\newcommand{\alephuv}{\textphnc{\ARaleph}$_{\mathrm{UV}}$}
%\newcommand{\alephha}{\textphnc{\ARaleph}$_{\mathrm{H}\alpha}$}
%\newcommand{\alephuvha}{\textphnc{\ARaleph}$_{0.66}$}
%\newcommand{\alephhb}{\textphnc{\ARaleph}$_{\mathrm{H}\beta}$}
\usepackage{lscape}
\usepackage{amsmath}
\newcommand{\alephuv}{f$_{\mathrm{esc}}$(0.16$\,\micron$)}
\newcommand{\alephha}{f$_{\mathrm{esc}}$(H$\alpha$)}
\newcommand{\alephuvha}{f$_{\mathrm{esc}}$(0.66$\,\micron$)}
\newcommand{\alephhb}{f$_{\mathrm{esc}}$(H$\beta$)}

@@

\altaffiltext{1}{Laboratoire AIM, DSM/Irfu/SAp, CEA-Saclay,
91191 Gif-sur-Yvette, France}
\altaffiltext{2}{National Optical Astronomy Observatory,
Tucson, AZ 85719, USA}
\altaffiltext{3}{Department of Astronomy, University of Arizona,
Tucson, AZ 85721, USA}
\altaffiltext{4}{Laboratoire d'Astrophysique de Marseille, Aix
Marseille Universit\'e, 13388 Marseille cedex 13, France}
\altaffiltext{5}{Department of Physics \& Astronomy, University of California
Irvine, Irvine, CA 92697, USA}
\altaffiltext{6}{Space Telescope Science Institute, Baltimore, MD 21218, USA}
\altaffiltext{7}{Department of Physics \& Astronomy, Texas A\&M University,
College Station, TX 77843, USA}
\altaffiltext{8}{Department of Astronomy, University of Massachusetts Amherst,
Amherst, MA 01003, USA}

@@

A galaxy's morphology is often defined as its spatial distribution of stars.
Rest-frame optical images of galaxies show diverse arrangements of
their stellar components: smooth ellipticals, tightly-wound spirals, clumpy
disks, barred disks, train-wrecks, fuzzballs, and whatever Willman 1 is
\citep{willman05,willman11}.
Little more than spatial extent is known about distributions of dust in dusty
galaxies
\citep{younger10,diaz10,simpson15}.  Yet spatial distributions of
all galactic components have intrinsic value.  If we want to learn about
galaxies, morphology should be a wavelength-independent word.  Surprises
surely abound: for example, galaxies at $z \sim 0.3$ have dust out to several
Mpc.  Their average dust mass profile is a constant fraction of their average
halo mass profile \citep[][see also \citealt{zaritsky94}]{menard10}.

@@

If we write this equation:
\begin{equation*}
L_{\mathrm{emergent}}/L_{\mathrm{intrinsic}} = 10^{-\mathrm{A}/2.5} = 10^{-\mathrm{E(B-V)} k(\lambda)/2.5}
\end{equation*}
we assume a uniform screen not because $k(\lambda)$ is solely dependent on
wavelength, but because $L_{\mathrm{emergent}}/L_{\mathrm{intrinsic}}$ is solely
dependent on
wavelength.  In an illustrative sense
$L_{\mathrm{emergent}}/L_{\mathrm{intrinsic}}$
is an attenuation formula convolved with a spatial distribution of dust.

@@

The discrepancy between the uniform assumption and real dust
distributions in low-redshift dust-poor galaxies grows even larger if we
consider that galaxies have centers and outskirts---that galaxies are not
point sources.  A number of studies find
that H$\alpha$ and UV attenuation decrease with increasing radius
\citep{boissier04,prescott07,munoz09}.  Ionizing stars are surrounded by more
dust than nonionizing UV-emitting stars; ionizing stars
at large radii have less dust than ionizing stars at small radii, and similarly
for nonionizing UV-emitting stars.

@@

Our study uses observations of the GOODS-S, COSMOS, and UDS regions.  A
catalog of \emph{Herschel}/PACS 100$\,\micron$ sources for GOODS-S comes from
\citet{magnelli13}; for COSMOS and UDS, we use catalogs produced for the
\emph{Herschel} survey of CANDELS regions (Inami et al., in prep).  A
100$\,\micron$ source is defined as a $\ge 3\sigma$ flux density measurement
from PSF fitting to a \emph{Spitzer}/MIPS 24$\,\micron$ source, which is based
on an IRAC 3.6$\,\micron$ source prior.  In GOODS-S, the catalog has
flux densities at 24, 70, 100, and 160$\,\micron$; in COSMOS and
UDS, the catalogs have flux densities at 24, 100, 160, 250, 350,
and 500$\,\micron$.  All flux densities are $\ge 3\sigma$.  We do not use the
250, 350, and 500$\,\micron$ flux
densities in the COSMOS and UDS catalogs, to avoid the effects of source
confusion on PSF fitting.  Including them changes our results negligibly.

@@

Some sources will be at $0.7 < z < 1.5$ but will not have visible H$\alpha$
line flux.  To determine line flux upper limits for these sources, we match each
100$\,\micron$ source to a source with a spectroscopic redshift in
the catalogs of: \citet{lefevre04,szokoly04,mignoli05,yamada05,ravikumar07,
vanzella08,lilly09,balestra10,fadda10,simpson12,kurk13,santini14}; Simpson et
al. (in prep.); Almaini et al. (in prep.); and
M. Dickinson (private communication).  Operationally both the
100$\,\micron$ and spectroscopic catalogs are matched to the CANDELS catalogs.
If the 100$\,\micron$ source has a spectroscopic redshift that is unconfirmed
by an uncontaminated grism spectrum, we estimate the widths of the invisible
Gaussian line profiles from the ratio of integrated flux density to peak
surface brightness for the region of the direct image surrounding the galaxy.
The direct
image is the image taken as part of the grism observations.  We then fit
the same model as above to the 1D spectrum and extract the H$\alpha$ line flux
uncertainty.  We use $5\sigma$ limits.  We are unable to determine limits for
galaxies observed by the grism that are undetected in the direct image.  Most
limits are in GOODS-S because the spectroscopic completeness is higher there
than it is in COSMOS or UDS.

@@

We use 24$\,\micron$ flux densities in the \emph{Spitzer} Heritage Archive.  Of
the 26 sources in \citet{overzier11}, 3 have unreliable 24$\,\micron$ flux
densities per the recommendations in the enhanced imaging products quick start
guide; these sources are excluded.  The remaining 23 galaxies have flux
densities at
0.15 and 0.23$\,\micron$ (NUV and FUV bands), from \emph{GALEX} observations.
H$\alpha$ line
fluxes, from SDSS observations, are from Overzier (private communication).  We
multiply the line fluxes by 1.67 as a fiber-aperture correction
\citep{overzier09}.

@@

We must exclude galaxies with active nuclei because fractions of their IR,
emergent UV, and emergent H$\alpha$ luminosities will be unrelated to newly
formed massive stars.  We identify 5 AGN hosts among the high-redshift dusty
galaxies; we use the \citet{donley12} criteria, which are based on mid-IR flux
densities, which all 3 CANDELS catalogs have.  These criteria will miss some
AGN hosts \citep{juneau13}.  We accept the contaminants because in some fields
we lack data---for example, X-ray data---that we could use to identify the
missed AGN hosts.

@@

Three star formation rates allow us to compare two attenuation values.
We eschew magnitude attenuation in favor of the escape fraction, which
is the ratio of emergent to intrinsic luminosity.  We define the following
quantities.
\begin{itemize}
\item \alephuv~is the escape fraction at rest-frame 0.16$\,\micron$.  In
relation to A$_{\mathrm{UV}}$,
f$_{\mathrm{esc}}$(0.16$\,\micron$) = 10$^{-\mathrm{A}_{\mathrm{UV}}/2.5}$.
\item \alephha~is the escape fraction of the H$\alpha$ line luminosity.
\item \alephuvha~is the escape fraction extrapolated from \alephuv~to the
wavelength of H$\alpha$---the attenuation formula prediction.  For the
attenuation formula in \citet{calzetti00}, \alephuvha~= \alephuv$^{0.33}$.
\end{itemize}

@@

\subsection{Reproducing the relation between escape fractions for dust-poor
galaxies}

The sample, from \citet{overzier11}, contains galaxies that lie roughly on
the low-redshift IRX-$\beta$ relation.  This relation is a blunt instrument we
use to determine whether or not galaxies obey an attenuation formula at UV
wavelengths; \alephuv~is a function of IRX and an attenuation formula relates
\alephuv~to $\beta$.  Since these galaxies lie on the relation, we
expect them to have dust properties that conform with the properties of
the galaxies in the \citet{calzetti00} sample.  We calculate \alephha~and
\alephuv~for each galaxy in the following way.
\begin{itemize}
\item \alephuv~= ($L_{\mathrm{IR}}$/($1.68\times0.16\times
L_{\mathrm{0.16}}$)+1)$^{-1}$.  This is equivalent to \alephuv~= (emergent UV
SFR)/(IR SFR + emergent UV SFR).
%\item \alephuvha~= \alephuv$^{0.33}$.
\item Following the assumptions in \ref{sfrs}: \alephha~=
(emergent H$\alpha$ SFR)/(IR SFR + emergent UV SFR).
\end{itemize}
We use these quantities to find, for the sample, a best-fit power-law index $q$
for the form \alephha~= \alephuv$^{q}$.

The top left panel of Fig. \ref{fha_fuv} shows that \alephha~= \alephuv$^{0.80}$
for the low-redshift
dust-poor galaxies.  If we use the IR and UV luminosities from
\citealt{overzier11}, \alephha~= \alephuv$^{0.84}$.  We lack
uncertainties on any SFRs so we also perform a robust linear regression,
which requires a fit to the form $\log\,$\alephha~= $q\,\log\,$\alephuv.  It
returns a similar result, as does a bootstrap resampling.  We recover a relation
close to the
\citet{calzetti97b} relation for similar galaxies, so we have some confidence
that our procedure is grossly correct.  We stress, again, that there are
no evolutionary connections between the low- and high-redshift galaxy samples;
we aim only to reproduce the \citet{calzetti97b} result with our nonstandard
method of determining \alephha.

@@

The top right panel of Fig. \ref{fha_fuv} shows that \alephha~=
\alephuv$^{0.55}$ for the low-redshift
dusty galaxies.  We use uncertainties only on the emergent H$\alpha$-derived
SFR---we treat it as the dependent variable---in the weighted fit.  The relation
for dust-poor galaxies is seemingly inapplicable to dusty galaxies at
low redshift.  In \S\ref{subsec:select} and \ref{sec:discuss} we explain why we
preface `inapplicable' with `seemingly.'

@@

The bottom left panel of Fig. \ref{fha_fuv} shows that \alephha~=
\alephuv$^{0.55}$ for high-redshift
dusty galaxies.  We leave limits out of this fit.  The uncertainty in
the index is very small; this is not surprising given the number of galaxies.
The dispersion about the best-fit relation is large; the central 50\% of
galaxies with H$\alpha$-detected SFRs lies between \alephha~= \alephuv$^{0.45}$
and \alephha~= \alephuv$^{0.66}$.  A survival regression, which incorporates
H$\alpha$ SFR limits in a fit to the form $\log\,$\alephha~=
$q\,\log\,$\alephuv, finds $q = 0.47$, as does a simple linear regression using
only the H$\alpha$-detected SFRs.  None of the galaxies have limits for both
the UV and H$\alpha$ SFRs.  The main effect of including limits in the
regression is to increase the standard error of the sample's best-fit index; a
marginally different index is a secondary effect.  Table \ref{regress}
summarizes the relevant quantities for the main fit to each sample of galaxies.

@@

\subsection{Issues with the regressions}\label{subsec:select}

@@

If we assume that dusty galaxies:
\begin{enumerate}
\item obey the \citet{calzetti00} attenuation formula; and
\item were to have the same UV spectrum in the absence of dust,
\end{enumerate}
our results indicate that their H$\alpha$ and 0.66$\,\micron$ escape
fractions disagree.  Unlike low-redshift dust-poor galaxies, dusty galaxies
have \alephha~= \alephuvha$^{1.6}$; like low-redshift dust-poor galaxies,
dusty galaxies have nonuniform dust distributions.  The relations between
\alephha~and \alephuvha~are similar to those found by \citet{onodera10},
\citet{kashino13}, and \citet{price13} and conflict with those of
\citet{erb06}.  These studies assume the applicability of the \citet{calzetti00}
attenuation
formula, and use samples of high-redshift galaxies that are not necessarily
dusty.  Their UV escape fractions come from stellar population modeling, while
ours come from IRX; their H$\alpha$ escape fractions come from ratios of
averaged H$\alpha$ to averaged H$\beta$ luminosities, or ratios of H$\alpha$ to
UV luminosities, while ours come from assumptions about SFRs.

@@

The dispersion about the best-fit relation for high-redshift dusty galaxies
is large, yet it is susceptible
to our possibly invalid assumption that a galaxy's instantaneous SFR has,
for at least $10^{8}$ yr, equaled its prolonged SFR.  For example, if most
massive stars formed over 15 Myr instead of 300 Myr, we should multiply
$L_{0.16}$ and $L_{\mathrm{IR}}$ by larger numbers than we do here to derive the
UV and IR SFRs.  The true UV SFR is 57\% higher and the true IR SFR is 63\%
higher \citep{madau14}.  The true UV escape fraction is little different;
because the true total SFR is higher, the true H$\alpha$ escape fraction is
lower.  Another scenario is that massive stars stopped forming within the last
15 Myr.  Perhaps some of the high-redshift dusty galaxies have
complicated star formation histories; the combined effect of deriving correct
SFRs might lead to lower dispersion.

There are few ways to resolve the uncertainties regarding star formation
histories and the applicability of the \citet{calzetti00} attenuation formula
to dusty galaxies.  One (partial) way is to use the formula and
\alephha~to predict the escape fraction of the H$\beta$ luminosity,
\alephhb.  The ratio of intrinsic
H$\alpha$ to H$\beta$ luminosities is 2.86 under reasonable
assumptions; with H$\beta$ observations, we can use
($L_{\mathrm{H}\alpha}$/$L_{\mathrm{H}\beta}$)/2.86~=~\alephha/\alephhb~and from this
determine \alephhb.  If the predicted and determined H$\beta$ escape fractions
agree, the assumed attenuation formula is probably valid at optical
wavelengths; the assumed star formation histories are also probably valid.
The histories are valid because the prediction is history-dependent and the
determination is history-independent---both line luminosities are from ionized
gas surrounding the same stars.  If
the predicted and determined fractions disagree, the attenuation
formula at optical wavelengths can be different for dusty galaxies
or their true \alephha~can be different.  The formula can differ due to dust
not distributed as a uniform foreground screen; see table 1 and fig. 3b of
\citealt{calzetti01}.  Fig. \ref{ahb}
shows this test applied to the low-redshift dusty galaxies.  To apply this
test to high-redshift dusty galaxies, we need near-IR spectra that cover
the H$\beta$ line.  If the dispersion
of H$\alpha$ escape fractions at a given UV escape fraction for high-redshift
dusty galaxies remains, there must be a diversity of dust
distributions.  Either way, this test provides no information on the relation
between UV and 0.66$\,\micron$ escape fractions; more extrapolations are
necessary to definitively interpret Fig. \ref{fha_fuv}.
